---
title: "MATH 324 Computer HW 1"
author: "Corey Russ"
date: 2018-02-14
output:
  html_document: default
  pdf_document: default
---

## Exercise 1: 
#### (a) Use c() to generate two datasets.

```{r}
modifiedMortar=c(16.85, 16.40, 17.21, 16.35, 16.52, 17.04, 16.96, 17.15, 16.59, 16.57)
unmodifiedMortar=c(16.62, 16.75, 17.37, 17.12, 16.98, 16.87, 17.34, 17.02, 17.08, 17.27)
```

#### (b) Use mean() and median() to calculate the mean and median of each dataset.

```{r}
mean(modifiedMortar)
median(modifiedMortar)

mean(unmodifiedMortar)
median(unmodifiedMortar)

```

#### (c) Use sd(), var() and IQR() to calculate the sample standard deviation, sample variance
#### and IQR of each dataset.

```{r}
sd(modifiedMortar)
var(modifiedMortar)
IQR(modifiedMortar)

sd(unmodifiedMortar)
var(unmodifiedMortar)
IQR(unmodifiedMortar)
```

#### (d) Construct the histograms for the two datasets and make comments about the shapes.

```{r}
hist(modifiedMortar)
hist(unmodifiedMortar)
```

The modified mortar has one cluster of data with higher frequency. The unmodified mortar is more spread out over all of the data.

#### (e) Construct comparative box-plots for the two groups and make comments about the
#### similarity and difference.

```{r}
boxplot(list(modifiedMortar=modifiedMortar, unmodifiedMortar=unmodifiedMortar), col="blue")
```

The median of the modified mortar is lower than the median of the unmodified mortar. The median of the unmodified mortar is the Q3 of modified mortar.

## Exercise 2:

#### (a) Use c() to generate the data.

```{r}
survey=c(4, 2, 3, 3, 1, 5, 4, 2, 2, 4, 
         5, 6, 4, 3, 3, 4, 4, 5, 6, 1, 
         2, 2, 3, 4, 3, 3, 5, 2, 1, 3)
```

#### (b) Construct the frequency table using table().

```{r}
table(survey)
```

#### (c) Construct pie chart using pie(). Add colors and title to the chart.

```{r}
pie(survey,labels=survey[1:30],col=rainbow(30), main="Number of Courses Taken per Student for 30 Students")
```

#### (d) Construct bar-plot using barplot(). Add color and title to the plot.

```{r}
barplot(survey, col=rainbow(30),main="Number of Courses Taken per Student")
```

#### (e) Use R functions to count how many students are taking more than three courses.

```{r}
sum(survey>3)
```

## Exercise 3:

#### (a) Use seq() to generate a sequence 2, 4, ..., 24.

```{r}
sequence=seq(2,12, by=2)
```

#### (b) Use log() to generate a new sequence where each element is log-transformed from the
#### sequence in (a).

```{r}
sequence=log10(sequence)
```

#### (c) Remove the second to fifth elements in the resulting sequence in (b).

```{r}
sequence=sequence[-(2:5)]
```

#### (d) Use length() to obtain the length of the resulting sequence in (c).
```{r}
length(sequence)
```

#### (e) Sort the resulting sequence in (d) from high to low using sort().
```{r}
sort(sequence, decreasing=TRUE)
```



